---
name: Taylor
surname: Heffer
position: "Assistant Professor"
address: "Ontario Tech University, Oshawa"
phone: +1 857 706 9988
email: "theffer@fas.harvard.edu"
github: tvheffer
orcid: 0000-0001-5586-5640
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
docname: CV
output: vitae::awesomecv
editor_options: 
  chunk_output_type: console
  format: pdf
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )
library(magrittr)
# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) %>%
  invisible()

source(file = here("r","data.r"))

```


# Academic Appointments

```{r APPOITNEMT}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Ontario Tech University", "2024-present", "Assistant Professor", "Oshawa, ON") %>%
  detailed_entries(Degree, Year, Institution, Where)

```

# Education and Training

```{r EDUCATION}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Harvard University", "2022-23", "Postdoctoral (NSERC) Fellow", "Cambridge, MA",
  "Brock University", "2017-22", "PhD, Lifespan Development Psychology", "St. Catharines, ON",
  "Brock University", "2015-17", "MA, Lifespan Development Psychology", "St. Catharines, ON",
  "Brock University", "2011-15", "BA, Honors Psychology and Child and Youth ", "St. Catharines, ON") %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Honors and Awards
**Academic and Research**

```{r AWARDS}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Harvard University", "2022", "Natural Sciences and Engineering Research Postdoctoral Fellowship", "Cambridge, MA", "Application ranked 1st in psychology",
  
 "Development Conference", "2022", "Student Presentation Award (Second Place)", "Alberta, Canada", NA,
 
 "Brock University", "2022", "Faculty of Social Science Research Assistantship ", NA, NA,
 "Brock University", "2022", "Susan Sydor Graduate Scholarship", NA, NA,
 "Brock University", "2021", "Ontario Graduate Scholarship", NA, NA,
 "Brock University", "2019", "Ralph D. Morris Graduate Student Award ", NA, NA,
 "Brock University", "2019", "Match of Minds", NA, NA,
 "Brock University", "2018-20", "Dean of Graduate Studies Excellence Scholarship", NA, NA,
 "Social Sciences and Humanities Research Council", "2017-20", "Joseph-Armand Bombardier Canada Graduate (PhD)", NA, NA,
 
 "Brock University", "2017", "Jack M. Miller Excellence in Research Award", NA, NA,
 "Brock University", "2017/20", "Distinguished Graduate Student Award MA and PhD", NA, NA,
 "Canadian Psychological Association", "2017", "Certificate of Academic Excellence (MA Thesis)", NA, NA,
 "Brock University", "2017", "Library Open Access Publishing Fund", NA, NA,	
 "Brock University", "2016", "Ontario Graduate Scholarship", NA, NA,
 "Social Sciences and Humanities Research Council", "2015", "Joseph-Armand Bombardier Canada Graduate Scholarship (MA)", NA, NA,
 "Brock University", "2015", "Research Fellowship & Match", NA, NA,
 "Brock University", "2015", "Entrance Scholarship", NA, NA,
 "Brock University", "2015", "Ontario Graduate Scholarship (Declined)", NA, NA) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
```
 
**Leadership and Community Engagement**
```{r L-AWARDS}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
 "Brock University", "2020/21", "Scotiabank Graduate Award ", NA, NA,
 "Brock University", "2020", "Barb Daly Excellence and Student Leadership", NA, NA,
 "Brock University", "2020", "Dr. Liette Vasseur Graduate Scholarship", NA, NA,
 "Brock University", "2020", "President Surgite Award", NA, NA,
 "Brock University", "2020", "Wendy Murphy Memorial Fund (Peer nominated)", NA, NA) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
```

# Publications

Refereed Published Academic Papers (19): 

1.	**Heffer, T**., Van Noordt S.J.R., & Willoughby, T. (2023). Developmental trajectories of sensitivity to threat in children and adolescents predict larger medial frontal theta differentiation during response inhibition. *Social Cognitive and Affective Neuroscience.* 

2.	Shahid, H., **Heffer, T**., Borg, M. E., \*Buma-Wiens, A., & Willoughby, T. (2022). Differentiating profiles of vaping, alcohol, and cannabis use among early adolescents. *The Journal of Early Adolescence.*

3.	Willoughby, T., **Heffer, T**., Borg, M. E. (2022). Deliberate Self-injury in Children and Associations with Negative Adjustment. *JAMA Pediatrics.*

4.	Van Noordt S.J.R., **Heffer, T**., Willoughby, T. (2021). A developmental examination of medial frontal theta dynamics and inhibitory control. *NeuroImage.*

5.	**Heffer, T.**, & Willoughby, T. (2021). Investigating the consistency of threat-related ERPs among children and adolescents. *Cognitive Affective Behavioral Neuroscience.*

6.	Willoughby, T., **Heffer, T**., Van Noordt S.J.R., Desjardins, J., Segalowitz, S., Schmidt, L. (2021). An ERP investigation of children and adolescents’ sensitivity to wins and losses during a peer observation manipulation. *Developmental Cognitive Neuroscience.*

7.	Willoughby, T., **Heffer, T**., Good, M., Magnacca, C. (2021). Is adolescence a time of heightened risk taking? An overview of types of risk-taking behaviors across age groups. *Developmental Review.* 

8.	Willoughby, T., Dykstra, V.W., **Heffer, T.**, \*Braccio., J. Shahid, H., (2021). A long-term study of what best predicts graduating from university versus leaving prior to graduation. *Journal of College Student Retention: Research, Theory & Practice.* 

9.	**Heffer, T**., \*Lundale, C., Wylie, B.E., Willoughby, T. (2021). Investigating sensitivity to threat with the Behavioral Inhibition Scale (BIS) among children, adolescents and adults: The role of negatively-phrased questions. *Personality and Individual Differences.*

10.	**Heffer, T**., & Willoughby, T. (2021). A person-centered examination of emotion dysregulation, sensitivity to threat, and impulsivity among children and adolescents: An ERP study. *Developmental Cognitive Neuroscience.*

11.	Willoughby, T., **Heffer, T**., Dykstra, V.W., Shahid, H., \*Braccio., J. (2020). A person-centred analysis of first-year university students: Associations with psychosocial adjustment across seven years and post-university outcomes. *Journal of Youth and Adolescence*. 49(12), 2459-2475.

12.	**Heffer, T**., & Willoughby, T. (2020). A longitudinal study investigating trajectories of sensitivity to threat and their association with alpha asymmetry among children and adolescents. *Developmental Cognitive Neuroscience*. 46, 100863. https://doi.org/10.1016/j.dcn.2020.100863

13.	**Heffer, T**., & Willoughby, T. (2020). Sensitivity to negative feedback among children and adolescents: An ERP study comparing developmental differences between high-worriers and low-worriers. *Cognitive, Affective, & Behavioral Neuroscience*, 20, 624-635. https://doi.org/10.3758/s13415-020-00791-8

14.	**Heffer, T**., Wylie, B.E, & Willoughby, T. (2019). An investigation of adolescents’ reported and self-perceived risk-taking. *The Journal of Early Adolescence*, 40(6), 772–788.

15.	**Heffer, T**., Good, M., Daly, O., MacDonell, E., Willoughby, T. (2019). The longitudinal association between social media use and depressive symptoms among adolescents and young adults: An empirical reply to Twenge et al. (2018). *Clinical Psychological Science*, 7(3), 462-470.
    - This work is included as one of the most read articles in this journal in the last 6 months

16.	**Heffer, T**., & Willoughby, T. (2018). The role of emotion dysregulation: A longitudinal investigation of the interpersonal theory of suicide. *Psychiatry Research*, 260, 379-383.

17.	**Heffer, T**., & Willoughby, T. (2017). A count of coping strategies: A longitudinal study investigating an alternative method to understanding coping and adjustment. *PloS one*, 12(10).

18.	Willoughby, T., **Heffer, T**., & Hamza C.A. (2015). The link between nonsuicidal self-injury and acquired capability for suicide: A longitudinal study. *Journal of Abnormal Psychology*, 1110-1115.

19.	Hamza, C. A., Willoughby, T., & **Heffer, T**. (2015). Impulsivity and nonsuicidal self-injury: A review and meta-analysis. *Clinical Psychology Review*, 3813-24. doi:10.1016/j.cpr.2015.02.010.

Non-refereed publications:

1.	Gallant, C., & **Heffer, T**. (2016). A Collaborative Approach to Graduate Training at Brock University. *Canadian Psychological Association*, Mind Pad.


# Presentations

**Invited Talks**

```{r TALKS}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
 "Ontario Tech University", "April 2023", "Psychology Department Research Talk", NA, NA,
 "Harvard University", "Feb 2021", "Affective Neuroscience and Development Lab", NA, NA,
 "University of Oregon", "Nov 2020", "Developing Brains in Context Lab", NA, NA,
 "Brock University", "2018/19/22", "Youth Engagement Committee", NA, "Invited to discuss research and facilitate youth involvement in research",
 "Psychology Society, Brock University", "March, 2018", "Panelist: Career Night", NA, NA,
 " Psychology Department, Brock University", "Nov, 2017", "Panelist: Graduate School Information Session", NA, NA,
 ) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
```


**Symposiums**

1.	Symposium Chair & Speaker. Factors that affect social behavior among children, adolescents, and emerging adults with anxiety-related temperament styles. Development 2022. (Alberta, Canada)
    - Awarded 2nd best student talk

**Conference Presentations**

1.	**Heffer, T**., Omary, A., Flournoy, J.C., Baum, G.L., Barch D.M., HCP-D Consortium, Somerville, L.H. (2023, March). The impact of reward and punishment history on response inhibition from childhood to early adulthood. Research accepted to the Society for Affective Science conference.

2.	Omary, A., **Heffer, T**., Flournoy, J. C., Baum, G. L., Curtis, M., Colich, N. L., Mair, P., Barch, D. M., HCP-D Consortium, & Somerville, L. H. (2023, April). Testing the mediating role of pubertal hormones on age-related changes and sex differences in adolescent behavioral inhibition and Activation [Poster presentation]. Social & Affective Neuroscience Society 2023 Conference.

3.	**Heffer, T**., van Noordt, S.J.R., Willoughby, T. (2021). The role of medial frontal theta among children and adolescents with consistently high threat sensitivity. Research presented at the Virtual FLUX Congress

4.	**Heffer, T**., Willoughby, T. (2021, April). Investigating the consistency of threat-related ERP’s among children and adolescents. Research presented to the Virtual Society for Research on Child Development Conference.

5.	**Heffer, T**., Willoughby, T. (2020, September). A person-centered examination of regulation, sensitivity to threat, and impulsivity among children and adolescents: An ERP study. Research accepted to the Virtual FLUX Congress.

6.	**Heffer, T**., Willoughby, T. (2020, canceled). Investigating Children and Adolescent Worriers’ Neural Sensitivity to Negative Feedback: Comparing Pubertal Status and Grade Level. Research accepted to Society for Research on Adolescence Conference, San Diego, CA.

7.	**Heffer, T**., Willoughby, T. (2019, September). Right Alpha Activation Moderates the Stability of Punishment Sensitivity Over Time. Research presented at Society for Psychophysiological Research Conference, Washington, DC.

8.	Willoughby, T., **Heffer, T**., van Noordt, S., Desjardins, J., Segalowitz, S., Schmidt, L. (2019, August). An ERP investigation of children and adolescents’ sensitivity to wins and losses during a perceived peer observation manipulation. Research presented at the FLUX Congress, New York, New York.

9.	**Heffer, T**., Willoughby, T. (2019, August). Investigating ERP Consistency across Child and Adolescent Worriers in Tasks Measuring Sensitivity to Punishment. Research presented at the FLUX Congress, New York, New York.

10.	**Heffer, T**., Willoughby, T. (2019, March). An ERP Study Investigating Sensitivity to Punishment among High and Low Worriers. Research presented at the Society for Research on Child Development Conference, Baltimore, Maryland.

11.	Wylie, B., **Heffer, T**., Willoughby, T. (2019, March). Adolescent Risk-Taking: A Comparison of Self-Reported Behaviors and Self-Perceptions. Research presented at the Society for Research on Child Development Conference, Baltimore, Maryland.

12.	Ilieff, M., Hamza, C. A., Willoughby, T. & **Heffer, T**. (2019, March). Maladaptive and adaptive perfectionism and nonsuicidal self-injury. Poster presented at the International Society for the Study of Self-Injury.

13.	**Heffer, T**., Willoughby, T. (2018, May). Investigating the Role of Worry in Children and Adolescents: An EEG Study. Symposium presented at Development 2018 Conference, Brock University.

14.	**Heffer, T**., Willoughby, T. (2018, May). Worry, Sleep Problems and Alcohol Use: A Longitudinal Study. Research presented at Development 2018 Conference, Brock University.

15.	Willoughby, T., Desjardins, J., Segalowitz, S., Schmidt, L., **Heffer, T**., Semplonius, T. (2018, May). An ERP Investigation of Children and Adolescents' Sensitivity to Wins and Losses during a Perceived Peer Observation Manipulation. Symposium presented at Development 2018 Conference, Brock University.

16.	**Heffer, T**., Willoughby, T. (2018, April). A Longitudinal Study of Emotion Regulation and Problem Behaviours. Research presented at Society for Research on Adolescence Conference, Minneapolis, Minnesota

17.	**Heffer, T**., Willoughby, T. (2017, May). The Role of Emotion Dysregulation: A Longitudinal Investigation of the Interpersonal Theory of Suicide. Research presented at Association for Psychological Science Conference, Boston, Massachusetts.

18.	**Heffer, T**., Willoughby, T. (2017, April). A Count of Coping Strategies: A Longitudinal Study Investigating Repertoire Richness and Adjustment. Research presented at Society for Research in Child Development Conference, Austin, Texas.

19.	**Heffer, T**., Willoughby, T. (2017, April). The Association between NSSI and Suicide Ideation: The role of Maladaptive Perfectionism. Research presented at Society for Research in Child Development Conference, Austin, Texas.

20.	**Heffer, T**., Willoughby, T., & Hamza C.A. (2016, March). The link between nonsuicidal self-injury and acquired capability for suicide: A longitudinal study. Research presented at the Society for Research on Adolescence Conference, Baltimore, Maryland. 

21.	**Heffer, T**., Willoughby, T., (2015, April). Investigating Joiner's Theory of Suicide: Identifying Predictors of Suicide Ideation in a Sample of University Students. Annual Ontario Psychology Undergraduate Thesis Conference, London, Ontario, Canada

# Teaching 

**Instructor Positions**
```{r Teaching}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
 "Brock University (Undergraduate 4th year course)", "Jan 2022", "Instructor: Data Science for Academic and Applied Research", NA, NA) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
```

```{r workshops}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
 "Brock University (4 workshops held)", "August 2022/23", "[R] is for research: A beginner’s guide to using R", NA, NA,
 ) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
```

**Invited Guest Lectures**
```{r lectures}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
 "Wesleyan University(Undergraduate 3rd year course)", "April 2023", "Adolescence and Emerging Adulthood", NA, NA,
 "Brock University(Undergraduate 4th year course)", "Nov 2020", "Data Science for Academic and Applied Research", NA, NA,
 "Brock University(Undergraduate 3rd year course)", "March 2019", "Adolescent Development ", NA, NA,
 ) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
```


**Other Teaching Activities**
```{r APPRENTICESHIP}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
 "Apprenticeship at Brock University (Undergraduate 4th year)", "Jan 2020/21", "Data Science for Academic and Applied Research", NA, NA,
 ) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
```



```{r}

brock <- c("PSYC 4P08: Data Science for Academic and Applied Research (2020/21)",
           "PSYC 2P12: Lifespan Development (2015/18/19)",
           "PSYC 4P07: Transition to workplace (2018)",
           "PSYC 3P39: Statistics (2016/17)",
           "PSYC 3P18: Adolescent Development (2016)",
           "PSYC 3P77: Social Development (2015)")

classes <- tibble(title =c(rep("Brock University", length(brock))), detail = brock, apprentice = "Teaching Assistantships")

classes %>%
  detailed_entries(
    what = title,
    why = detail, 
    with= apprentice[1]
  )
```

```{r other-teach}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
 "ANDL, Harvard University", "2022", "Project Teach", NA, "Co-created and taught a seminar for 7th grade students on developmental cognitive neuroscience topics",
 
  "Namibia, Africa", "2013", "Resiliency Class: Brock University", NA, "Created and taught lessons in Math/English to grades 8-12 for three weeks",
 ) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
```

# Mentoring
**Undergraduate Students**
\vspace{-5truemm}
```{r}
harvard <- c("Jadyn Matthews (Honors thesis)","Nicole Uribe (Research Assistant)")
brock <- c("Cody Ellis (Honors thesis)", "Annelise Wiens (Honors thesis & Independent study)",
           "Joelle Braccio (Independent study)", "Carly Lundale (Honors thesis & Independent study)")

classes <- tibble(title =c((rep("Harvard University", length(harvard))),rep("Brock University", length(brock))), detail = c(harvard,brock))

classes %>%
  detailed_entries(
    what = title,
    why = detail, 

  ) 
classes[c(1:4),3] <- ""
    
```

**Honors & Distinctions Awarded to Mentees** 

```{r mentee-award}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
 "Annelise Wiens, Brock University", "2021", "Faculty of Social Science Student Research Award", NA, NA,
 "Carly Lundale, Canadian Psychological Association", "2020", "Honors thesis: Certificate of Excellence", NA, NA) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
```

# Knowledge Mobilization

```{r km}
leadership <- tribble(
    ~title, ~unit, ~year,  ~detail,
    "Community Research Talk", "Pathstone Mental Health", "2019", "presented research to over 100 staff at Pathstone Mental Health",
    "Infographics", "Brock Healthy Youth Project Partners (e.g., WHO; UNICEF, Mental Health Commission of Canada; Niagara region school board)", "2019", NA,
    "Media Interviews", "Heffer et al., 2019; Clin.Psyc.Sci.", "2019", 
    "The results from one of my first-author publications was distributed widely and received extensive media attention, as follows:
    \\begin{itemize}
        \\item Association for Psychological Science. (2019, February 27). Longitudinal Data Show No Evidence of Teens’ Social Media Use Leading to Depression. Retrieved from https://www.psychologicalscience.org/observer/longitudinal-data-show-no-evidence-of-teens-social-media-use-leading-to-depression (also featured in Science Daily)
        \\item Psychology Today. (2019, February 22). Is Tech Really Hurting Teens?[Press release]. 
        Retrieved from: https://www.psychologytoday.com/ us/blog/brainstorm/201902/is-tech-really-hurting-teens.
        \\item Brock News. (2019, February 14). Brock researchers find no evidence social media use predicts future depression. [Press release]. Retrieved from: https://brocku.ca/brock-news/2019/02/brock-researchers-find-no-evidence-social-media-use-predicts-future-depression
     \\item Also distributed in Curaçao Chronicle, Psych Central, Medical News Today, Drugs.com, Consumer Affairs; Daily Mail, The Times, etc.
    \\end{itemize}")

leadership %>%
    detailed_entries(
        with = title,
        what = unit,
        why = detail,
        when = year, .protect = F)

```

# Research and Teaching Development
```{r training}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
 "Center for Brain Science, Harvard", "2022", "Introduction to fMRI", NA, NA,
 "Harvard University", "2022", "Bystander intervention training", NA, NA,
 "Brock University", "2021", "Using R for Reproducible Research Course", NA, NA,
 "Virtual", "2021", "Global R Studio Conference", NA, NA,
 "Harvard’s Women in Psyc", "2021", "Advanced R workshop: A Tidyverse Language Perspective ", NA, NA,
 "Informal R Users Group at Brock University", "2019/20", "ARGH Coding Club", NA, NA,
 "Brock University", "2019", "Datathon R Workshop", NA, NA,
 "Brock University", "2017-19", "EEG Workshop", NA, "One-week workshop focusing on EEG analysis",
 "Mindware Technologies, Ohio", "2018", "Impedance Workshop", NA, "Two-day workshop on data collection and data cleaning",
 "Brock University", "2018", "Data Visualization and Programing Workshop", NA, "Two-day workshop using Python for data visualization",
 "Brock University(grad-level course)", "2018", "Introduction to Computer Programming for Experimental Psychology", NA, "Introduction to MATLAB programming language",
 "Centre for Pedagogical Innovation, Brock University", "2017", "TA Advanced Certificate in Teaching and Learning in Higher Education", NA, NA,
 "Centre for Pedagogical Innovation, Brock University", "2016", "TA Certificate in Teaching and Learning in Higher Education", NA, NA,
  "Brock University(grad-level course)", "2016", "Longitudinal Data Analysis", NA, NA,
  "Brock University", "2015", "3-day R Workshop", NA, NA,
 ) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
``` 

# Service

```{r leader }
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Harvard University", "2022-23", "Mentorship meetups (Committee Member)", NA, NA,
  "Brock University", "2016-21", "Undergraduate Workshops", NA, "Created and facilitated annual workshops (e.g., Thinking about Grad school?; Getting Involved in Research; External Scholarship Applications)",
 "Brock University", "2017-22", "Psychology Social Committee (Committee Member)", NA, NA,
 "Brock University", "2020", "Brock University Featured Graduate Student", NA, NA,
 "Brock University", "2018", "Development 2018 Psychology Conference (Volunteer)", NA, NA,
 "Brock University", "2017-18", "Psychology Department Recruitment Group (Committee Member)", NA, NA,
 "Canadian Psychological Association", "2016-19", "Psychology Social Committee (Graduate Student Representative)", NA, NA,
 "Brock University", "2016-17", "Psychology Graduate Committee (Graduate Student Representative)", NA, NA,
 "Brock University", "2016-19", "Recruitment Events (Graduate Student Volunteer)", NA, NA,
 "Brock University", "2015-16", "Psychology Department Committee (Graduate Student Representative)", NA, NA,
 ) %>%
  detailed_entries(Degree, Year, Institution, Where, Why)
``` 



